No Evidence for Lunar Transit in New Analysis of HST Observations of the Kepler-1625 System

### 2019-05-21 apj_v3/ms.tex
revised version

We used the following priors: the stellar radius was normally distributed, $R_* \sim N(1.81, 0.17) R_\odot$ (see next section). The planet radius was uniform from $8 - 14R_\oplus$. The planet transit time was uniform over the timespan of the observations, and inclination was uniform from $0 - 90^\circ$.  The planet mass was log-normally distributed, $M_\mathrm{p} \sim 10^{2.5 \pm 0.5} M_\oplus$, based on the expectation for Jupiter-radius objects from \cite{ning18}.  For the moon model, we allowed the transit time to vary uniformly over the entire visit. The moon period was uniform between 1.6 to 260 days. These limits span the duration of the \HST\ observations (so there is one possible moon occultation event), to the orbit at 0.5 the Hill radius, based on the stability limit for prograde moon orbits \citep{domingos06}. The Hill radius calculation assumed the planet and stellar masses are $1\,M_\mathrm{Jup}$ and $1.37\,M_\odot$.  The moon mass varied uniformly from $0 - 30 M_\oplus$. The longitude of the ascending node was also uniform from $0 - 360^\circ$.  The moon inclination was uniform from $0 - 90^\circ$,  and was defined relative to that of the planet. A $90^\circ$ inclined orbit has an impact parameter of zero on the disk of the planet. We assigned zero prior probability to scenarios where the moon did not transit or experienced a grazing transit. We made this choice to put an upper limit on the radius of a fully transiting moon; for grazing transits or non-transits the moon radius could be arbitrarily large.

>>>>

We used the following priors: the stellar radius was normally distributed, $R_* \sim N(1.81, 0.17) R_\odot$ (see next section). The planet radius was uniform from $8 - 14R_\oplus$. The planet transit time was uniform over the timespan of the observations, and inclination was uniform from $0 - 90^\circ$.  The planet mass was log-normally distributed, $M_\mathrm{p} \sim 10^{2.5 \pm 0.5} M_\oplus$, based on the expectation for Jupiter-radius objects from \cite{ning18}.  For the moon model, we allowed the transit time to vary uniformly over the entire visit. The moon period was uniform between 1.6 to 260 days. These limits span the duration of the \HST\ observations (so there is one possible moon occultation event), to the orbit at 0.5 the Hill radius, based on the stability limit for prograde moon orbits \citep{domingos06}. The Hill radius calculation assumed the planet and stellar masses are $1\,M_\mathrm{Jup}$ and $1.37\,M_\odot$.  The moon mass varied uniformly from $0 - 30 M_\oplus$. The longitude of the ascending node was also uniform from $0 - 360^\circ$.  The moon inclination was uniform from $0 - 90^\circ$,  and was defined relative to the \added{line of sight}. \deleted{A $90^\circ$ inclined orbit has an impact parameter of zero on the disk of the planet.} We assigned zero prior probability to scenarios where the moon did not transit or experienced a grazing transit. We made this choice to put an upper limit on the radius of a fully transiting moon; for grazing transits or non-transits the moon radius could be arbitrarily large.
